A thesis draft

### 2018-11-24 res/sections/07-Introduction.tex
Fix thesis name and supervisor
Add some intro
New intro

 % This is just a draft, nothing suitable for the final product: sources are in
 % form of a todo

 % --- INTRODUCTION ---
\chapter{Introduction}
\label{chap:intro}

 Through the history of internet, many factors changed and new innovations came,
 but at the end of the day a fundamental key remains: connection performances
 are, indeed, what the users really want. With the arrival of mobile
 connectivity, wireless networks started to have an important role in everyone's
 life. In this context network efficiency is a decisive factor in the
 development of new connectivity standards (e.g 2G, 3G, LTE) and in the creation
 of ad-hoc transmission protocols (i.e. TCP versions specialized to exploit the
 characteristic of wireless networks, such as Hybla and Vegas). It is for this
 reason that, beside improved radio communications, back-end infrastructure
 began to be refined too. During their communication to the destination packets
 are elaborated, compressed and processed in order to make their transmission as
 fast as possible. On top of that, mobile traffic is continuously surging every
 year, with the backbones having more and more data to deliver, making
 in-hardware backbone solutions less efficient. Their time-to-deploy, in fact,
 is very high compared to the requirements of the network. With this trend,
 in-hardware solutions will not be able to keep up. Is with this considerations
 that a software approach is being proposed to become the new way to deploy
 network components. While less efficient, they are faster to bring them up,
 offering an unprecedented flexibility~\cite{nguyen2017sdn}. Furthermore, new
 virtualization technologies such as Cloud computing and Docker are becoming
 more and more mature for being employed in large-scale production environments,
 where new frameworks, called orchestrators (e.g. Kubernetes, Docker Swarm),
 allow to easily manage the application lifecycle, i.e. deployment, scale
 up/down and finally, removal.

 \newpage

 \section{Document organization}

>>>>

\chapter{Introduction}
\label{chap:intro}

Through the history of Internet, many factors changed and new innovations came,
but at the end of the day a fundamental key remains: connection performances
are, indeed, what the users really want.
Today, connectivity plays an important role in everyone's life. Several decades 
brought solutions with enhanced wired and wireless connectivity, like 
Ethernet, Fast Ethernet, 2G, 3G, LTE, and better communication protocols such 
as a whole plethora of TCP standards in order to keep up with the continuous 
surging of network traffic. Internet Service Providers to be able to 
efficiently process the whole quantity of packets passing through the network, 
applies several optimizations along the packet path. Until this day, these 
optimizations have mostly been based on costly, in hardware solutions. In 
particular, these Network Functions are able to perform only generic packet 
elaboration, since they do not know the Quality of Service required by every 
connection. It is in this context that 5G proposes a new way to approach 
networking, suggesting the virtualization of this Network Functions, making 
their deployments faster and cheaper. On top of that, it proposes specific 
services for determined kind of data. If in the past a train running a 
300km/h had to use the same network services of an IoT device sending data 
updates every hour, now 5G proposes two different and efficient solutions for 
this completely different services. This separation is performed through the 
creation of determined network components called Network Slices. This new 
possibility of offering the network with specialized class of services, 
combined with emerging virtualization technologies like cloud computing, 
hypervisor-virtualized machine or container-based solutions enables the 
deployment of Virtualized Network Functions within seconds running on generic 
purpose or custom hardware. While there may be some performances degreadations, 
it has been demonstrated that their time-to-deploy and the possibility of 
automation they offers are unprecedented~\cite{nguyen2017sdn}. On top of 
that, specialized software acts as a MANager and Orchestrator (MANO) for this 
VNFs, regulating their lifecycle. While most of the current proposals are based 
on hypervisor on cloud solutions, in this thesis we are going to see a 
proof-of-concept of a part of a Network Slice, equipped with a custom MANO 
solution, based on the new container-based technology, called Docker, on a 
recent orchestrator framework: Kubernetes.

\section*{Document organization}
